### 2021-03-27 treatise-pdflatex/2_problem_setting.tex
Section 3.2: change dimension

For simplicity we suppose uniform linear arrays, for which the response would be,
%
\DispNum {a:y':CN:NH} {
\V {a} \SB {\psi'}
= \frac {1} {\R {N_H}} \sum_{n_h=0}^{N_H-1} \mathsf {e} ^{\mathsf {i} n_h \psi'} \V {u} _{n_h}
\in \mathbb {C} ^ {N_H} 
}
%
where \m {\mathsf {e}} is the base of natural logarithm, and \m {\mathsf {i}} the imaginary unit.

And consider the virtual representation of the MIMO channel, as in Akdeniz et.\ al.\ \cite {ALS14},
%
\DispNum {H:H:l0:ql} {
\M {H}
=\sum_{l=0} ^{L-1}
\a_l
\V {a} \SB { 2\pi \frac {d_{\mathrm {arr}}} {\l _{\mathrm {arr}}} \sin \f_l'}
\V {a} \SB { 2\pi \frac {d_{\mathrm {arr}}} {\l _{\mathrm {arr}}} \sin \th_l'}^\dagger 
}
%
The physical meaning of \m {\f_l'} is the \m {l}-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \m {\th_l'}, the \m {l}-th angle of arrival wave, and \m {d_{\mathrm {arr}}} is the distance between two adjacent antennae.
For our purpose, we may absorb the arguments of \m {\V {a}}
%
\DispNum {f:l:2p:2p} {
\f_l
= &2\pi \frac {d_{\mathrm {arr}}} {\l_{\mathrm {arr}}} \sin \f_l'
  \; \mathrm {Mod}\; \RB {2\pi} \\
%
\th_l
= &2\pi \frac {d_{\mathrm {arr}}} {\l_{\mathrm {arr}}} \sin \th_l'
  \; \mathrm {Mod}\; \RB {2\pi} 
}
%
to get a simpler form
%
\DispNum {H:H:l0:NH} {
\M {H}
=\sum_{l=0} ^{L-1} \a_l \V {a} \SB {\f_l} \V {a} \SB {\th_l}^\Adj
\in \mathbb {C} ^{N_H \D N_H} 
}

@@

We consider hybrid beamforming at both the transmitter and receiver ends, as shown in Figure 2.
Each end consists of both digital and analog precoders and combiners.
In the transmitter end, there are (seeing towards the receiver end), the digital precoder \m {\M {F} _B \in \mathbb {C} ^{N_{B,t} \D N_{B,t}}} and the analog precoder \m {\M {F} _R \in \mathbb {C} ^{N_H \D N_{B,t}}}.
Similarly, in the receiver end, there are (seeing towards the transmitter end) the digital combiner \m {\M {W} _B \in \mathbb {C} ^{N_{B,r} \D N_{B,r}}} and the analog combiner \m {\M {W} _R \in \mathbb {C} ^{N_{B,r} \D N_H}}.

Recall that analog precoders may only have values of unity magnitude,
%
\DispNum {F:R:1::R1} {
\Nm {\RB {\M {F} _R} _{\SB {n_H, n_{R,t}}}}
= &1, \\
%
\Nm {\RB {\M {W} _R} _{\SB {n_{R,r}, n_H}}}
= &1, \\
%
n_H
= &0, \dots N_H-1, \\
%
n_{R,t}
= &0, \dots N_{B,t}-1  \\
%
n_{R,r}
= &0, \dots N_{B,r}-1 
}
%
And we assume
%
\DispNum {N:H:NY:NY} {
N_H \gg N_{B,t}, N_{B,r}
}

Since we restrict our discussion to a short interval of time, the noise term may be simply taken as a matrix \m {\M {Z} \in \mathbb {C} ^{N_H \D N_{B,t}}} with each entry being i.i.d.\ standard normal.
Let us introduce the effective channel
%
\DispNum {Y:Y:WB:BZ} {
\M {Y}
:=\M {W} _B \M {W} _R \RB {\M {H} \M {F} _R \M {F} _B +\M {Z}} 
}
%
Our task then amounts to recovering \m {\M {H}}, and generating \m {\M {W} _R}, \m {\M {W} _B}, \m {\M {F} _R}, and \m {\M {F} _B}.

@@

It is more appealing to write
%
\DispNum {h:h:ve:Nh} {
\V {h}
:= &\mathrm {vec} \SB {\M {H}}
\in \mathbb {C} ^{N_H^2} \\
%
\V {y}
:= &\mathrm {vec} \SB {\M {Y}}
\in \mathbb {C} ^{N_{B,t} N_{B,r}} \\
%
\V {z}
:= &\mathrm {vec} \SB {\M {W} _B \M {W} _R \M {Z}}
\in \mathbb {C} ^{N_{B,t} N_{B,r}} \\
%
\M {Q}
:= &\RB {\M {F} _B^\intercal \M {F} _R^\Tr} \otimes \RB {\M {W} _B \M {W} _R}
\in \mathbb {C} ^{N_{B,t} N_{B,r} \D N_H^2} 
}
%
to formulate the problem as a linear system:
%
\DispNum {y:y:Qh:hz} {
\V {y}
=\M {Q} \V {h} +\V {z} 
}
%
At this stage, we intend to apply DS, but there is no guarantee that \m {\V {h}} must be sparse.

@@

Denote the discrete Fourier transform matrix to be \m {\M {K}},
%
\DispNum {K:K:CN:H1} {
\M {K} \in &\mathbb {C} ^{N_H \D N_H} \notag \\
%
\M {K} _{\SB {n_1, n_2}}
= &\frac {1} {\R {N_H}} \mathsf {e}^{2\pi \mathsf {i} n_1 n_2 /N_H}, \notag \\
%
\quad n_1, n_2
= &0, 1, \dots, N_H-1 
}
%
Recall that we have
%
\DispNum {K:K:I:::I} {
\M {K}^\dagger \M {K}
= \M {I} 
}
%
If we write
%
\DispNum {G:G:KH:HK} {
\M {G}
=\M {K}^\dagger \M {H} \M {K} 
}
%
then \m {\M {G}} can be interpreted as spatial frequency domain representation of \m {\M {H}}.
%
\DispNum {Y:Y:WB:NY} {
\M {Y}
=\M {W} _B \M {W} _R \M {K} \D \M {G} \D \M {K}^\dagger \M {F} _R \M {F} _B
+\M {W} _B \M {W} _R \M {Z}
\in \mathbb {C} ^{N_{B,r} \D N_{B,t}} 
}
%
If we are sure that \m {\M {G}} is sparse, then we recover \m {\M {G}} instead.
Set for brevity
%
\DispNum {P:P:FB:Nh} {
\M {P}
:=\RB {\M {F} _B^\intercal \M {F} _R^\intercal \M {K}^\ast} \otimes \RB {\M {W} _B \M {W} _R \M {K}}
\in \mathbb {C} ^{N_{B,t} N_{B,r} \D N_H^2} 
}
%
and
%
\DispNum {g:g:ve:Nh} {
\V {g}
:= \mathrm {vec} \SB {\M {G}}
\in \mathbb {C} ^ {N_H \D N_H} 
}
%
accordingly
%
\DispNum {y:y:Pg:gz} {
\V {y}
=\M {P} \V {g} +\V {z} 
}

@@

\Result
{Algorithm}
{
\begin {itemize}
%
\item Let \m {\g_{\mathrm {DS}} \geq 0} be given.
%
\item Input \m {\M {F} _B \in \mathbb {C} ^{N_R \D N_{B,t}}},
\m {\M {F} _R \in \mathbb {C} ^{N_H \D N_R}},
\m {\M {W} _R \in \mathbb {C} ^{N_R \D N_H}},
\m {\M {W} _B \in \mathbb {C} ^{N_{B,r} \D N_R}},
and \m {\M {Y} \in \mathbb {C} ^{N_{B,r} \D N_{B,t}}}.
%
\item Find \m {\M {P} \in \mathbb {C} ^{N_{B,r} N_{B,t} \D N_H^2}}, \m {\V {y} \in \mathbb {C} ^{N_H^2}} as in above.
%
\item Compute the convex program
%
\DispNum {g:g:mi:DS} {
\hat {\V {g}}
\leftarrow \begin {cases}
\Min {\V {g}' \in \mathbb {C} ^{N_H^2}} & \VNm {\V {g}'} _1 \\
%
\mathrm {subject} \; \mathrm {to} \quad & \VNm {\M {P}^\dagger \RB {\V {y} -\M {P} \V {g}'}} _\infty \leq \g_{\mathrm {DS}} \\
\end {cases} 
}
%
\item Convert \m {\hat {\V {g}}} back to the space domain, namely
%
\Disp {
\hat {\M {G}}
\leftarrow \mathrm {vec}^{-1} \SB {\hat {\V {g}}} 
}
%
\item Recover the estimated \m {\hat {\M {H}}}, as
%
\Disp {
\hat {\M {H}}
\leftarrow \M {K} \hat {\M {G}} \M {K}^\dagger 
}
%
\item Output \m {\hat {\M {H}}}.
%
\end {itemize}
}

>>>>

For simplicity we suppose uniform linear arrays, for which the response would be,
%
\DispNum {a:y':CN:NH} {
\V {a} \SB {\psi', N}
= \frac {1} {\R {N}} \sum_{n_h=0}^{N-1} \mathsf {e} ^{\mathsf {i} n_h \psi'} \V {u} _{n_h}
\in \mathbb {C} ^ {N} 
}
%
where \m {\mathsf {e}} is the base of natural logarithm, and \m {\mathsf {i}} the imaginary unit.

And consider the virtual representation of the MIMO channel, as in Akdeniz et.\ al.\ \cite {ALS14},
%
\DispNum {H:H:l0:ql} {
\M {H}
=\sum_{l=0} ^{L-1}
\a_l
\V {a} \SB { 2\pi \frac {d_{\mathrm {arr}}} {\l _{\mathrm {arr}}} \sin \f_l', N_{H,r}}
\V {a} \SB { 2\pi \frac {d_{\mathrm {arr}}} {\l _{\mathrm {arr}}} \sin \th_l', N_{H,r}}^\dagger 
}
%
The physical meaning of \m {\f_l'} is the \m {l}-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \m {\th_l'}, the \m {l}-th angle of arrival wave, and \m {d_{\mathrm {arr}}} is the distance between two adjacent antennae.
For our purpose, we may absorb the arguments of \m {\V {a}}
%
\DispNum {f:l:2p:2p} {
\f_l
= &2\pi \frac {d_{\mathrm {arr}}} {\l_{\mathrm {arr}}} \sin \f_l'
  \; \mathrm {Mod}\; \RB {2\pi} \\
%
\th_l
= &2\pi \frac {d_{\mathrm {arr}}} {\l_{\mathrm {arr}}} \sin \th_l'
  \; \mathrm {Mod}\; \RB {2\pi} 
}
%
to get a simpler form
%
\DispNum {H:H:l0:NH} {
\M {H}
=\sum_{l=0} ^{L-1} \a_l \V {a} \SB {\f_l} \V {a} \SB {\th_l}^\Adj
\in \mathbb {C} ^{N_{H,r} \D N_{H,t}} 
}

@@

We consider hybrid beamforming at both the transmitter and receiver ends, as shown in Figure 2.
Each end consists of both digital and analog precoders and combiners.
In the transmitter end, there are (seeing towards the receiver end), the digital precoder \m {\M {F} _B \in \mathbb {C} ^{N_B \D N_B}} and the analog precoder \m {\M {F} _R \in \mathbb {C} ^{N_{H,t} \D N_B}}.
Similarly, in the receiver end, there are (seeing towards the transmitter end) the digital combiner \m {\M {W} _B \in \mathbb {C} ^{N_B \D N_B}} and the analog combiner \m {\M {W} _R \in \mathbb {C} ^{N_B \D N_{H,r}}}.

Recall that analog precoders may only have values of unity magnitude,
%
\DispNum {F:R:1::R1} {
\Nm {\RB {\M {F} _R} _{\SB {n_H, n_{R,t}}}}
= &1, \\
%
\Nm {\RB {\M {W} _R} _{\SB {n_{R,r}, n_H}}}
= &1, \\
%
n_{H,t}
= &0, \dots N_{H,t}-1, \\
%
n_{H,r}
= &0, \dots N_{H,r}-1, \\
%
n_{R,t}
= &0, \dots N_B-1  \\
%
n_{R,r}
= &0, \dots N_B-1 
}
%
And we assume
%
\DispNum {N:H:NY:NY} {
N_{H,t}, N_{H,t} \gg N_B, N_B
}

Since we restrict our discussion to a short interval of time, the noise term may be simply taken as a matrix \m {\M {Z} \in \mathbb {C} ^{N_B \D N_B}} with each entry being i.i.d.\ standard normal.
Let us introduce the effective channel
%
\DispNum {Y:Y:WB:BZ} {
\M {Y}
:=\M {W} _B \M {W} _R \RB {\M {H} \M {F} _R \M {F} _B +\M {Z}} 
}
%
Our task then amounts to recovering \m {\M {H}}, and generating \m {\M {W} _R}, \m {\M {W} _B}, \m {\M {F} _R}, and \m {\M {F} _B}.

@@

It is more appealing to write
%
\DispNum {h:h:ve:Nh} {
\V {h}
:= &\mathrm {vec} \SB {\M {H}}
\in \mathbb {C} ^{N_{H,t} N_{H,r}} \\
%
\V {y}
:= &\mathrm {vec} \SB {\M {Y}}
\in \mathbb {C} ^{N_B N_B} \\
%
\V {z}
:= &\mathrm {vec} \SB {\M {W} _B \M {W} _R \M {Z}}
\in \mathbb {C} ^{N_B N_B} \\
%
\M {Q}
:= &\RB {\M {F} _B^\intercal \M {F} _R^\Tr} \otimes \RB {\M {W} _B \M {W} _R}
\in \mathbb {C} ^{N_B N_B \D N_{H,t} N_{H,r}} 
}
%
to formulate the problem as a linear system:
%
\DispNum {y:y:Qh:hz} {
\V {y}
=\M {Q} \V {h} +\V {z} 
}
%
At this stage, we intend to apply DS, but there is no guarantee that \m {\V {h}} must be sparse.

@@

Denote the discrete Fourier transform matrix to be \m {\M {K}},
%
\DispNum {K:K:CN:H1} {
\M {K} \in &\mathbb {C} ^{N_{H,t} \D N_{H,r}} \notag \\
%
\M {K} _{\SB {n_1, n_2}} \SB {N}
= &\frac {1} {\R {N}} \mathsf {e}^{2\pi \mathsf {i} n_1 n_2 /N}, \notag \\
%
\quad n_1, n_2
= &0, 1, \dots, N-1 
}
%
Recall that we have
%
\DispNum {K:K:I:::I} {
\M {K}^\dagger \M {K}
= \M {I} 
}
%
If we write
%
\DispNum {G:G:KH:HK} {
\M {G}
=\M {K}^\dagger \M {H} \M {K} 
}
%
then \m {\M {G}} can be interpreted as spatial frequency domain representation of \m {\M {H}}.
%
\DispNum {Y:Y:WB:NY} {
\M {Y}
=\M {W} _B \M {W} _R \M {K} \D \M {G} \D \M {K}^\dagger \M {F} _R \M {F} _B
+\M {W} _B \M {W} _R \M {Z}
\in \mathbb {C} ^{N_B \D N_B} 
}
%
If we are sure that \m {\M {G}} is sparse, then we recover \m {\M {G}} instead.
Set for brevity
%
\DispNum {P:P:FB:Nh} {
\M {P}
:=\RB {\M {F} _B^\intercal \M {F} _R^\intercal \M {K}^\ast} \otimes \RB {\M {W} _B \M {W} _R \M {K}}
\in \mathbb {C} ^{N_B N_B \D N_{H,t} N_{H,r}} 
}
%
and
%
\DispNum {g:g:ve:Nh} {
\V {g}
:= \mathrm {vec} \SB {\M {G}}
\in \mathbb {C} ^ {N_{H,t} \D N_{H,r}} 
}
%
accordingly
%
\DispNum {y:y:Pg:gz} {
\V {y}
=\M {P} \V {g} +\V {z} 
}

@@

\Result
{Algorithm}
{
\begin {itemize}
%
\item Let \m {\g_{\mathrm {DS}} \geq 0} be given.
%
\item Input \m {\M {F} _B \in \mathbb {C} ^{N_{R,t} \D N_B}},
\m {\M {F} _R \in \mathbb {C} ^{N_{H,t} \D N_R}},
\m {\M {W} _R \in \mathbb {C} ^{N_{R,r} \D N_{H,r}}},
\m {\M {W} _B \in \mathbb {C} ^{N_B \D N_{R,r}}},
and \m {\M {Y} \in \mathbb {C} ^{N_B \D N_B}}.
%
\item Find \m {\M {P} \in \mathbb {C} ^{N_B N_B \D N_{H,t} N_{H,r}}}, \m {\V {y} \in \mathbb {C} ^{N_{H,t} N_{H,r}}} as in above.
%
\item Compute the convex program
%
\DispNum {g:g:mi:DS} {
\hat {\V {g}}
\leftarrow \begin {cases}
\Min {\V {g}' \in \mathbb {C} ^{N_{H,t} N_{H,r}}} & \VNm {\V {g}'} _1 \\
%
\mathrm {subject} \; \mathrm {to} \quad & \VNm {\M {P}^\dagger \RB {\V {y} -\M {P} \V {g}'}} _\infty \leq \g_{\mathrm {DS}} \\
\end {cases} 
}
%
\item Convert \m {\hat {\V {g}}} back to the space domain, namely
%
\Disp {
\hat {\M {G}}
\leftarrow \mathrm {vec}^{-1} \SB {\hat {\V {g}}} 
}
%
\item Recover the estimated \m {\hat {\M {H}}}, as
%
\Disp {
\hat {\M {H}}
\leftarrow \M {K} \hat {\M {G}} \M {K}^\dagger 
}
%
\item Output \m {\hat {\M {H}}}.
%
\end {itemize}
}

### 2021-03-27 treatise-pdflatex/3_1_sparsity_of_channel.tex
LaTeX: align equations
minor typos
Section 3.2: change dimension

We hope that \m {\VNm {\V {g} _{\SB{\mathcal {C}}}} _1} is small.
If so, we shall substitute the quantity into the expected square error of DS, thus generalizing to the almost-sparse case.
Recall that \m {\M {G}} is just the vectorization of \m {\V {g}}, and is the function of \m {\V {a}}, so we seek to establish that \m {\V {a}} is almost sparse.
We define, similarly, \m {\V {a} _{\SB{\mathcal {A}}}} and \m {\V {a} _{\SB{\mathcal {C}}}}, with sparsity level \m {s} different from \m {S}.
If \m {N_H} is large, we may forget for a moment that \m {s} is an integer.

First, we investigate
%
\DispNum {a:2:Ka:22} {
\VNm {\V {a} \SB {\f} _{\SB{\mathcal {C}}}} _2 ^2
=\VNm {\RB {\M {K}^\dagger \V {a} \SB {\f}} _{\SB{\mathcal {C}}}} _2 ^2 
}
%
Let \m {\f} be fixed.
Towards that end, introduce
%
\DispNum {y':H:f'M:p'p'} {
\psi \SB {\f, n_H}
:=\RB {
   \f \; \mathrm {Mod}\; \frac {2\pi} {N_H}
   + \RB {\frac {2 n_H} {N_H} + 1} \pi
} \;
\mathrm {Mod}\; \RB {2\pi}
- \pi 
}
%
Note that by construction
%
\DispNum {y':H:p'::p':} {
\Nm {\psi \SB {\f, n_H}}
\leq \pi 
}
%
And set for short
%
\DispNum {D:y':nH:Hy'} {
D \SB {\psi'}
:= \sum_{n_H=0}^{N_H-1} \mathsf {e}^{i n_H \psi'} 
}
%
And
%
\DispNum {b:f':Ka:af'} {
\V {b} \SB {\f}
=\M {K}^\dagger \V {a} \SB {\f} 
}
%
Then observe
%
\DispNum {K:H:1N:nH} {
\V {b} \SB {\f} _{\SB {n_H}}
=\frac {1} {N_H} D \SB {\psi \SB {\f, n_H}} 
}

By the nature of alternating series, for \m {- \pi \leq x < \pi}, it holds that
%
\DispNum {x:6:si:nx} {
\Nm {x - \frac {x^3} {6}}
\leq \Nm {\sin x}. 
}
Therefore,
%
\DispNum {D:y':si:y'p'} {
\Nm {D \SB {\psi'}}
= \frac {\Nm {\sin \SB {N_H \psi'/2}}} {\Nm {\sin \SB {\psi' /2}}} \\
%
\leq B \SB {\psi'} \\
%
:= \frac {48} {\Nm {\psi'^2 -24} \Nm {\psi'}}, \\
%
- \pi \leq \psi' < \pi. 
}
%
Combining \eqref {y':H:f'M:p'p'}, \eqref {K:H:1N:nH}, and \eqref {D:y':si:y'p'} we have
%
\DispNum {b:1:1N:C1} {
\VNm {\V {b} \SB {\f} _{\SB{\mathcal {C}}}} _1
\leq \frac {1} {N_H}
\VNm {
\RB {
   \sum_{n_H' =0}^{N_H -1}
      B \SB {\psi \SB {\f, n_H'}}
      \V {u} _{n_H'}
} _{\SB{\mathcal {C}}}
} _1
}

Note that \m {\Nm {B \SB {\psi'}}} is strictly decreasing in \m {\SB {0,\pi}}.
We are going to bound the rectangles by an integral, where we have to split the cases that \m {N_H} is odd and even.
%
\DispNum {b:1:1N:NH} {
\VNm {\V {b} \SB {\f} _{\SB{\mathcal {C}}}} _1
\leq \frac {1} {N_H} \D \frac {N_H} {2\pi} \D 2 \int_{\pi s/N_H}^{\pi} B \SB {\psi'} ^2 d \psi' \\
%
= \frac {48} {N_H \pi^3}
\int _{s /N_H} ^1 \frac {1} {\RB {24/\pi^2 -x'^2} ^2 x'^2} dx' \\
%
=\frac {1} {\pi} \log \frac {N_H^2 /s^2 - \pi^2 /24} {1 - \pi^2 /24} \\
%
\eqsim \frac {2} {\pi} \RB {\log N_H - \log s} \\
%
\leq \frac {2} {\pi} \log N_H 
}
%
Since the value of \m {s} is at our disposal, we choose
%
\DispNum {s:s:lo:NH} {
s
=\R {\log N_H} 
}
%
so that, by \m {\ell_p}-norm inequality, we have the following estimation.

\Result
{Proposition}
{
Let \m {\f } be given, and linear array response in spacial frequency domain \m {\V {b} \SB {\f}} defined in \eqref {b:f':Ka:af'}.
Then, for any random instance of \m {\f},
%
\DispNum {a:2:4N:NH} {
\VNm {\V {b} \SB {\f} _{\SB{\mathcal {C}}}} _1
\leq \frac {2} {\pi} \log N_H 
}
}

@@

If we further choose that
\DispNum {S:S:Ls:s2} {
S
=L s^2 
}
by triangle inequality, by the property of Frobenius norm,
%
\DispNum {g:1:l0:a'1} {
\VNm {\V {g} _{\SB{\mathcal {C}}}} _1
\leq 
\sum _{l=0} ^{L-1} \Nm {\a_l}
\VNm {\V {b} \SB {\f_l} _{\SB{\mathcal {C}}}} _1
\VNm {\V {b} \SB {\th_l} _{\SB{\mathcal {C}}}} _1 \\
%
\leq 
\VNm {\V {b} \SB {\f_l} _{\SB{\mathcal {C}}}} _1
\VNm {\V {b} \SB {\th_l} _{\SB{\mathcal {C}}}} _1
\sum _{l=0} ^{L-1} \Nm {\a_l} \\
%
\leq 
\frac {4} {\pi^2} L \RB {\log N_H}^2 \D
\frac {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l} 
}
%
Then observe that
%
\DispNum {E:1:2p':2p'} {
\mathbb {E} \SB {\frac {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l}}
=\frac{\R {2}} {\R {\pi}} 
}
By Hoeffding inequality,
%
\DispNum {P:p':2e:3p'} {
\mathbb {P} \SB {
   \frac {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l}
   \geq \frac {4 \R{2}} {\R {\pi}}
}
\leq 2 \exp \SB {- \frac {9L} {\pi}} 
}
%
Now we have
\DispNum {g:2:12:43} {
\frac {\VNm {\M {g} _{\SB{\mathcal {C}}}} _1} {\RB {\log N_H}^2}
\leq \frac {12 \R{2}} {\pi ^{5/2}}
\leq \frac {4} {3}. 
}
%
\Result
{Proposition}
{
Let \m {\V {g} \in \mathbb {C} ^{N_H^2}} be defined as in \eqref {g:g:ve:Nh}.
Then the bound
%
\DispNum {g:C:4p':NH} {
\VNm {\M {g} _{\SB{\mathcal {C}}}} _1
\leq \frac {4} {3} \RB {\log N_H}^2 
}
%
holds for probability \m {p}, with
%
\DispNum {1:p:1N:H3} {
1 -p
\leq 2 \exp \SB {- \frac {9L} {\pi}} 
}
}

>>>>

We hope that \m {\VNm {\V {g} _{\SB{\mathcal {C}}}} _1} is small.
If so, we shall substitute the quantity into the expected square error of DS, thus generalizing to the almost-sparse case.
Recall that \m {\M {G}} is just the vectorization of \m {\V {g}}, and is the function of \m {\V {a}}, so we seek to establish that \m {\V {a}} is almost sparse.
We define, similarly, \m {\V {a} _{\SB{\mathcal {A}}}} and \m {\V {a} _{\SB{\mathcal {C}}}}, with sparsity level \m {s} different from \m {S}.
If \m {N} is large, we may forget for a moment that \m {s} is an integer.

First, we investigate
%
\DispNum {a:2:Ka:22} {
\VNm {\V {a} \SB {\f} _{\SB{\mathcal {C}}}} _2 ^2
=\VNm {\RB {\M {K}^\dagger \V {a} \SB {\f}} _{\SB{\mathcal {C}}}} _2 ^2 
}
%
Let \m {\f} be fixed.
Towards that end, introduce
%
\DispNum {y':H:f'M:p'p'} {
\psi \SB {\f, n_H}
:=\RB {
   \f \; \mathrm {Mod}\; \frac {2\pi} {N}
   + \RB {\frac {2 n_H} {N} + 1} \pi
} \;
\mathrm {Mod}\; \RB {2\pi}
- \pi 
}
%
Note that by construction
%
\DispNum {y':H:p'::p':} {
\Nm {\psi \SB {\f, n_H}}
\leq \pi 
}
%
And set for short
%
\DispNum {D:y':nH:Hy'} {
D \SB {\psi'}
:= \sum_{n_H=0}^{N-1} \mathsf {e}^{i n_H \psi'} 
}
%
And
%
\DispNum {b:f':Ka:af'} {
\V {b} \SB {\f}
=\M {K}^\dagger \V {a} \SB {\f} 
}
%
Then observe
%
\DispNum {K:H:1N:nH} {
\V {b} \SB {\f} _{\SB {n_H}}
=\frac {1} {N} D \SB {\psi \SB {\f, n_H}} 
}

By the nature of alternating series, for \m {- \pi \leq x < \pi}, it holds that
%
\DispNum {x:6:si:nx} {
\Nm {x - \frac {x^3} {6}}
\leq \Nm {\sin x}. 
}
Therefore,
%
\DispNum {D:y':si:y'p'} {
\Nm {D \SB {\psi'}}
= &\frac {\Nm {\sin \SB {N \psi'/2}}} {\Nm {\sin \SB {\psi' /2}}} \notag \\
%
\leq &B \SB {\psi'} \notag \\
%
:= &\frac {48} {\Nm {\psi'^2 -24} \Nm {\psi'}}, \notag \\
%
- \pi \leq &\psi' < \pi. 
}
%
Combining \eqref {y':H:f'M:p'p'}, \eqref {K:H:1N:nH}, and \eqref {D:y':si:y'p'} we have
%
\DispNum {b:1:1N:C1} {
\VNm {\V {b} \SB {\f} _{\SB{\mathcal {C}}}} _1
\leq \frac {1} {N}
\VNm {
\RB {
   \sum_{n_H' =0}^{N -1}
      B \SB {\psi \SB {\f, n_H'}}
      \V {u} _{n_H'}
} _{\SB{\mathcal {C}}}
} _1
}

Note that \m {\Nm {B \SB {\psi'}}} is strictly decreasing in \m {\SB {0,\pi}}.
We are going to bound the rectangles by an integral, where we have to split the cases that \m {N} is odd and even.
%
\DispNum {b:1:1N:NH} {
\VNm {\V {b} \SB {\f} _{\SB{\mathcal {C}}}} _1
\leq &\frac {1} {N} \D \frac {N} {2\pi} \D 2 \int_{\pi s/N}^{\pi} B \SB {\psi'} ^2 d \psi' \notag \\
%
= &\frac {48} {N \pi^3}
\int _{s /N} ^1 \frac {1} {\RB {24/\pi^2 -x'^2} ^2 x'^2} dx' \notag \\
%
= &\frac {1} {\pi} \log \frac {N^2 /s^2 - \pi^2 /24} {1 - \pi^2 /24} \notag \\
%
\eqsim &\frac {2} {\pi} \RB {\log N - \log s} \notag \\
%
\leq &\frac {2} {\pi} \log N 
}
%
Since the value of \m {s} is at our disposal, we choose
%
\DispNum {s:s:lo:NH} {
s
=\R {\log N} 
}
%
so that, by \m {\ell_p}-norm inequality, we have the following estimation.

\Result
{Proposition}
{
Let \m {\f } be given, and linear array response in spacial frequency domain \m {\V {b} \SB {\f}} defined in \eqref {b:f':Ka:af'}.
Then, for any random instance of \m {\f},
%
\DispNum {a:2:4N:NH} {
\VNm {\V {b} \SB {\f} _{\SB{\mathcal {C}}}} _1
\leq \frac {2} {\pi} \log N 
}
}

@@

If we further choose that
\DispNum {S:S:Ls:s2} {
S
=L s^2 
}
by triangle inequality, by the property of Frobenius norm,
%
\DispNum {g:1:l0:a'1} {
\VNm {\V {g} _{\SB{\mathcal {C}}}} _1
\leq 
&\sum _{l=0} ^{L-1} \Nm {\a_l}
\VNm {\V {b} \SB {\f_l} _{\SB{\mathcal {C}}}} _1
\VNm {\V {b} \SB {\th_l} _{\SB{\mathcal {C}}}} _1 \notag \\
%
\leq 
&\frac {4} {\pi^2} L \RB {\log N_{H,t}} \RB {\log N_{H,r}} \D
\frac {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l} 
}
%
Then observe that
%
\DispNum {E:1:2p':2p'} {
\mathbb {E} \SB {\frac {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l}}
=\frac{\R {2}} {\R {\pi}} 
}
By Hoeffding inequality,
%
\DispNum {P:p':2e:3p'} {
\mathbb {P} \SB {
   \frac {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l}
   \geq \frac {4 \R{2}} {\R {\pi}}
}
\leq 2 \exp \SB {- \frac {9L} {\pi}} 
}
%
Now we have
\DispNum {g:2:12:43} {
\frac {\VNm {\M {g} _{\SB{\mathcal {C}}}} _1} {\RB {\log N_{H,t}} \RB {\log N_{H,r}}}
\leq \frac {12 \R{2}} {\pi ^{5/2}}
\leq \frac {4} {3}. 
}
%
\Result
{Proposition}
{
Let \m {\V {g} \in \mathbb {C} ^{N_{H,t} \D N_{H,r}}} be defined as in \eqref {g:g:ve:Nh}.
Then the bound
%
\DispNum {g:C:4p':NH} {
\VNm {\M {g} _{\SB{\mathcal {C}}}} _1
\leq \frac {4} {3} \RB {\log N_{H,t}} \RB {\log N_{H,r}} 
}
%
holds for probability \m {p}, with
%
\DispNum {1:p:1N:H3} {
1 -p
\leq 2 \exp \SB {- \frac {9L} {\pi}} 
}
}
